Decorrelating Errors in Quantum Gates by Random Gate Synthesis

### 2018-07-23 decorrelation/decorrelation.tex
changin out a picture, changing text, adding in needcites

\begin{abstract}
Thresholds for fault-tolerant quantum computation are often calculated assuming a noise model in which errors are uncorrelated. While convenient for simulation, these error models are often unphysical. Recent work by Preskill and others has shown that arbitrarily long computations may be performed even in the presence of spatial correlation, provided the correlation is sufficiently weak and decays sufficiently quickly with distance, but at the cost of a significantly lower threshold. The success of algebraic decorrelation methods, such as dynamical decoupling, demonstrate that quantum control techniques are capable of reducing temporal noise correlations. We propose to introduce similar methods to effect the spatial decorrelation of errors in quantum circuits, thereby increasing the threshold for fault-tolerant computation in such systems.
\end{abstract}

@@

Steady progress has been made in the theory of quantum error correction, proving higher thresholds for increasingly general models of noise \cite{Aharonov2006}. These results show that quantum computation is feasible, however recent NISQ \cite{Preskill2018} devices have noise that is not only often above thresholds, but that also violates assumptions made by the models used in proofs.

As an example, many models assume that errors are local, however systems can have spatially correlated error on more than two qubits that arise from multi-qubit terms in the Hamiltonian, such as:
\begin{equation}\label{eq:0}
  H(t) = \sum_{n}\sum_{i}\sum_{j=x,y,z} a^{\textbf{i}}_{\textbf{j}}(t)(\sigma_{j_1}^{i_1}\otimes\sigma_{j_2}^{i_2}\otimes ... \otimes \sigma_{j_n}^{i_n})
\end{equation}
where $a^{\textbf{i}}_{\textbf{j}}$ is a stochastic process. In a standard nearest-neighbors topology, like those found in super-conducting qubit architectures, these terms might arise from an effective model where high-frequency degrees of freedom are intergrated out to yield high-weight operators. These noise channels are one way in which the assumptions used in proofs of thresholds may be violated.

Another assumption that is instrumental in proving many threshold theorems is Markovianity \cite{Kitaev1997}. There are many ways in which devices can behave in non-Markovian ways, and NISQ devices have already been shown to be subject to drift in controls, \cite{Kelly2018} and in general non-Markovian noise \cite{BlumeKohout2017}. Other authors have tried to address these problems \cite{Wallman2016, Campbell2017, Heim2016} by using circuit composition to try to remove correlated noise. Indeed, other have even implemented these routines natively in hardware \cite{Ware2018}. These routines all require some level of sophistication. In the case of \cite{Campbell2017}, the analysis assumes some algorithm for decomposing arbitray unitaries, and treats Pauli and Clifford gates as being free to implement in those decompositions, which is far from the reality of modern quantum computers. In \cite{Wallman2016} and the implementation in \cite{Ware2018}, the random frames are implemented in each sequence by precompiling the inserted Pauli frame rotations with the Clifford operations. In general, this cannot be done efficiently for non-Clifford operations, and in addition, this introduces a linear-time precompilation overhead for shot of the circuit.

To remedy these problems, we take a different approach and propose to inject additional decorrelating randomness into the system through the use of \emph{balanced control solutions} (BCSs). BCSs are families of control solutions that all approximate the same target gate, but with balanced errors for any given instance of the noise Hamiltonian. That is, for a target gate, $U_T$, we seek a family of control solutions, $c_i(t)$, each implementing an approximation $U_i$ to the target gate, such that the family of unitary approximations is \emph{balanced}. A balanced family is one which satisfies, for some small $\alpha$,
\begin{equation}\label{eq:1}
  \frac{1}{N}\sum_{i=1}^N \omega_i U_i \rho U_i^\dagger = DPN[\alpha]\left(U_T \rho U_T^\dagger \right)
\end{equation}

@@

For example, randomized benchmarking and tomography will report incorrect answers without any syndrome \cite{Merkel2013}, and gateset tomography will report that the gateset failed to be Markovian, but will fail to diagnose in what way it was non-Markovian. Because BCSs change the error to a depolorizing channel, the correlations in the noise can be massively reduced, and the process can be made much closer to Markovian, at no real cost to the fidelity of the implemented gate. Unlike \cite{Ware2018}, \cite{Wallman2016}, and \citep{Campbell2017}, this routine can be implemented natively in the control electronics of a quantum computer, and only requires that the onboard sequencer has the abiltiy to generate random numbers - no pre or post processing is required.

@@

In general these gradients can be computed by propagating partial derivatives of the cost function with respect to control parameters through each timestep of the  via the chain rule. However, in \cite{Khaneja2005} Khaneja et al. derive a simple update formula that is correct to first order. In particular one can show that:
\begin{align}
\frac{\partial J(U)}{\partial u_{ij}} = -2Re\{\braket{{U_{j+1}^{\dagger}...U_N^{\dagger} U_T}}{i\Delta tH_jU_j...U_1}\\
\braket{U_j...U_1}{U_{j+1}^{\dagger}...U_N^{\dagger} U_T}\} +  \mathcal{O}(\Delta t^2)
\end{align}

In this paper we have modified the update step to use instead use approximately the following gradient:
\begin{align}\label{quadrature}
\int p(\vec{\delta})\frac{\partial J(U(\vec{\delta}))}{\partial u_{ij}} d\vec{\delta}
\end{align}
with $p(\vec{\delta})$ Gaussian distributed. This technique has been used in previous works such as \cite{Goerz2014} to ensure that the optimal control results are robust over a wide range of errors, and we approximate this integral approximately in this paper by using Gaussian quadrature. Doing this ensures that the family of controls produced by our routine perform moderately well over a range of stochastic errors.

\section{Optimal Control Problem}\label{ocp}
\subsection{Random Gate Synthesis}
To explore the utility of BCSs, we consider the following Hamiltonian:
\begin{equation}\label{eq:2}
  H(t) = H_0 + \sum_{i=1}^n (c_i(t) + \delta_i(t))H_i
\end{equation}
for control Hamiltonians $H_i$, free evolution Hamiltonian $H_0$ and time-varying random variables $\delta_i$. Such a model might describe a superconducting qubit quantum processor where control amplitudes for the RF pulses vary over time. Correlations between different $\delta_i$ might arise if two of the controls have the same noise source. Examples of shared noise sources include $X$ and $Y$ gates in superconducting qubit architectures might use the same AWG and pulse envelope, and diurnal temperature drift of control electronics.
\subsection{Channel Approximation}
After using GRAPE or another optimal control routine to synthesize a collection of controls, we must find the weights $w_i$ such that the collection of controls form a BCS as described in (\ref{eq:1}). To do this, for each control $U_i$ we find the unitary error channel $\mathcal{E}_i$ such that $\mathcal{E}_iU_i=U_T$, where $U_T$ is the target gate. If we consider the Pauli-Liouville representation of this error channel, the diagonal terms are the \textit{stochastic} terms that arise from classical uncertainty, while the off-diagonal terms may more generally arise from \textit{coherent} operations. In particular, we see that we can write a convex sum over these channels as:
\begin{align}
 \frac{1}{N} \sum^N_{i=1} w_i \mathcal{E}^{\dagger} (U_T\rho U_T^{\dagger}) \mathcal{E}
\end{align}
Now, to approximate a depolarizing channel we define our optimal control problem to be the following, which minimizes the off-diagonal terms:
\begin{equation}\label{eq:minimization}
  \begin{split}
    &\underset{w_0, ..., w_N}{\textbf{minimize}} \{\sum_{i\neq j}^N|\sigma_i\Lambda(\sigma_j)|^2\}\\
    &\textbf{where}\ \Lambda(\sigma_j) := \sum^N_{i=1}w_i\mathcal{E}_i^{\dagger}\sigma_j\mathcal{E}_i\\
    &\textbf{subject to} \sum_{i=1}^Nw_i = 1
  \end{split}
\end{equation}

@@

Previous authors have considered minimizing the diamond distance to the nearest Pauli or Clifford Channel \cite{Magesan2013}, and while this gives a good theoretical framework, it requires the use of a convex solver, and in particular does not have the restriction that the optimal channel be decomposable into a given family of controls. Our routine, on the other hand, uses a convex optimization routine to compute the diamond norm to needing to computing a sum. In the next section we give a simple example, followed by numerical results for one qubit and two qubits gates in sections \ref{1Q Gates} and \ref{2Q Gates}.

@@

\section{A Simple Example}
As a somewhat trivial example, consider a single-qubit rotation-angle error, such as result from stochastic laser amplitude fluctuations. A BCS may consist of an $X_\pi$ pulse, as well as an $\bar X_\pi$ pulse (i.e., a clockwise and counter clockwise rotation of the qubit). In the case of excess amplitude, the $X_\pi$ pulse will result in an over-rotation error, while the $\bar X_\pi$ pulse results in an \emph{under}-rotation error. When it comes time to perform the target gate in a quantum circuit, one member of the BCS is chosen uniformly at random. This has the effect of decreasing the norm of the noise channel and decorrelating the over-rotation error (Figure \ref{fig:simple_example}). In this simple example, we can solve the minimization problem given by equation \ref{eq:minimization} analytically. In particular, if we choose the weights in \ref{eq:1} such that $\omega_i=1$, and we choose to represent ou gates in the vectorized superoperator representation, then:

\begin{equation}
  \begin{gathered}
    \frac{1}{2}(X_{\pi + \epsilon} + \bar X_{\pi + \epsilon}) \\  
    = (\sin^2{\frac{\pi + \epsilon}{2}}I + \cos^2{\frac{\pi + \epsilon}{2}}X)X \\
    \approx ((1 - \epsilon^2)I + \epsilon^2X)X
  \end{gathered}
\end{equation}

@@

\section{Numerical Results}\label{numerical}
\subsection{1Q Gates}\label{1Q Gates}
 In this section, we present numerical results on generating one-qubit gates that together with $RZ(\theta$) rotations are universal for one-qubit computation. Our control Hamiltonian is given as: 
\begin{equation}\label{eq:1Qham}
  H = \epsilon\sigma_z + (1 + \delta)(c_x(t)\sigma_x + c_y(t)\sigma_y)
\end{equation}
$\epsilon$ is a normally distributed random variable, centered at $0$ with standard deviation $.001$, corresponding to a time varying Stark shift on the qubit. $\delta$ is also a normally distributed random variable with the same parameters, and is meant to represent random fluctuations in the control electronics, such as diurnal variations resulting from temperature instability. We assume that the errors on $\sigma_x$ and $\sigma_y$ are perfecly correlated, as mentioned in Section \ref{ocp}.
[ADD ANALYSIS OF PLOTS]
\begin{figure*}
\centering
\includegraphics[width=\textwidth]{x2.png}
\caption{In the above we have used our method to produce a BCS for a $RX(\frac{\pi}{2})$ pulse, with the Hamiltonian given in \ref{eq:1Qham}. A) shows the sum of the squared norms of the off diagonal terms in the Pauli Transfer Matrix of $\mathcal{E}$. B) gives the corresponding infidelity for each member of the BCS, and the optimal choice of weights.}
\end{figure*}

@@

\subsection{2Q Gates}\label{2Q Gates}
 In this section, we present numerical results on a generating one and two-qubit gates that together with $RZ(\theta)$ rotations are universal for two-qubit computation. Our control Hamiltonian is given as: 
\begin{equation} \label{eq:2Qham}
H = \exp{(-i\frac{\sigma_z^1\otimes\sigma_z^2}{4})} + \sum_{j=1}^2(\epsilon_j\sigma_z^j + (1 + \delta_j)(c_x^jx(t)\sigma_x^j + c_y^j(t)\sigma_y^j))
\end{equation}
We again assume that the standard deviations are $.001$ on all parameters $\delta_j$ and $c^j_i$ and that errors on the single qubit $\sigma_x$ and $\sigma_y$ rotations are perfectly correlated.
[ADD ANALYSIS OF PLOTS]
%These plots take a little while to make, so I can't iterate *that* fast - clearly the fonts need to be bigger, and there should be a title what else add a legend saying the black is the optimal?
\begin{figure*}[t]
\centering
\includegraphics[width=\textwidth]{2Q.png}
\caption{In the above we have used our method to produce a BCS for a ZZ($\frac{\pi}{2}$) entangling gate with controls given by \ref{eq:2Qham}. A) shows the sum of the squared norms of the off diagonal terms in the Pauli Transfer Matrix of $\mathcal{E}$. B) gives the corresponding infidelity for each member of the BCS, and the optimal choice of weights.}
\end{figure*}

>>>>

\begin{abstract}
Thresholds for fault-tolerant quantum computation are often calculated assuming a noise model in which errors are uncorrelated. While convenient for simulation, these error models are often unphysical. Work by Preskill and others has shown that arbitrarily long computations may be performed even in the presence of spatial correlation, provided the correlation is sufficiently weak and decays sufficiently quickly with distance, but at the cost of a significantly lower threshold. The success of algebraic decorrelation methods, such as dynamical decoupling, demonstrate that quantum control techniques are capable of reducing temporal noise correlations. We propose to introduce similar methods to effect the spatial decorrelation of errors in quantum circuits, thereby increasing the threshold for fault-tolerant computation in such systems.
\end{abstract}

@@

Steady progress has been made in the theory of quantum error correction, proving higher thresholds for increasingly general models of noise \cite{Aharonov2006}\needcite. These results show that quantum computation is feasible, however recent NISQ \cite{Preskill2018} devices have noise that is not only often above thresholds, but that also violates fundamental assumptions made by the models used in these results, such as Markovianity \cite{Kitaev1997} , independance of errors \needcite , and even the magnitude of the noise \needcite . With these assumptions violated, promises about system performance cannot be made as easily.

%As an example, many models assume that errors are local, however systems can have spatially correlated error on more than two qubits that arise from multi-qubit terms in the Hamiltonian, such as:
%\begin{equation}\label{eq:0}
%  H(t) = \sum_{n}\sum_{i}\sum_{j=x,y,z} a^{\textbf{i}}_{\textbf{j}}(t)(\sigma_{j_1}^{i_1}\otimes\sigma_{j_2}^{i_2}\otimes ... \otimes \sigma_{j_n}^{i_n})
%\end{equation}
%where $a^{\textbf{i}}_{\textbf{j}}$ is a stochastic process. In a standard nearest-neighbors topology, like those found in super-conducting qubit architectures, these terms might arise from an effective model where high-frequency degrees of freedom are intergrated out to yield high-weight operators. These noise channels are one way in which the assumptions used in proofs of thresholds may be violated.

As examples of these deviations from the theory, there are many ways in which devices can behave in non-Markovian ways, such as drift in controls, \cite{Kelly2018} and general non-Markovian noise \cite{BlumeKohout2017}. Even if a given system behaves in a Markovian way, many models make simplifying assumptions about the noise on that system - such as positing that it has a simple structure. Because of its  classical simulability, the channel that is often chosen is the Pauli channel \needcite . From there, one can ask what models can honestly be represented by using these simple models \needcite, but the fundamental problem with this approach is the pessimism that comes along with it. As we get closer to having real, usable systems, we want models that not only give us guarantees, but faithfully represent our system.

Other authors have tried to address these problems \cite{Wallman2016, Campbell2017, Heim2016} by using circuit composition to try to remove correlated noise. Given a process that is generated by a sequence of channels with some unknown, potentially channel depdenent error, the realization has been made that coherent error in the process can be averaged away into incoherent error, at the cost of an additional compilation step. Some of these routines have even been demonstrated experiementally \cite{Ware2018}, and been shown to reduce the off diagonal elements in the Pauli Liouville representation \needcite of the channels.

A common feature of these routines is that take advantage of the fact that processes are generally enacted as a sequence of gates. By inserting a potentially expensive classical pre-compilation step, they can exploit sequence structure of a process to average away coherent error. In the case of \cite{Campbell2017}, the analysis takes the point of view of treating Pauli and Clifford gates as being free, which is out of reach of modern quantum computers\needcite. In \cite{Wallman2016} and the implementation in \cite{Ware2018}, the random frames are implemented in each sequence by precompiling the inserted Pauli frame rotations with the Clifford operations. In general, this cannot be done efficiently for non-Clifford operations, and there for this routine is demanding given the severe circuit depth constraints of modern quantum computers.\needcite

To remedy these problems, we take a different approach at the gate synthesis level. We propose to inject additional decorrelating randomness into the system through the use of \emph{balanced control solutions} (BCSs). BCSs are families of control solutions that all approximate the same target gate, but with balanced errors for any given instance of the noise Hamiltonian. That is, for a target gate, $U_T$, we seek a family of control solutions, $c_i(t)$, each implementing an approximation $U_i$ to the target gate, such that the family of unitary approximations is \emph{balanced}. A balanced family is one which satisfies, for some small $\alpha$,
\begin{equation}\label{eq:1}
  \frac{1}{N}\sum_{i=1}^N \omega_i U_i \rho U_i^\dagger = DPN[\alpha]\left(U_T \rho U_T^\dagger \right)
\end{equation}

@@

For example, randomized benchmarking and tomography will report incorrect answers without any syndrome \cite{Merkel2013}, and gateset tomography will report that the gateset failed to be Markovian, but will fail to diagnose in what way it was non-Markovian. Because BCSs change the error to a depolorizing channel, the correlations in the noise can be massively reduced, and the process can be made much closer to Markovian, at no real cost to the fidelity of the implemented gate. Unlike in \cite{Wallman2016, Campbell2017, Ware2018} this routine can be implemented natively in control electronics, and only requires that the onboard sequencer has the abiltiy to generate random numbers - no pre or post processing is required.

@@

In general these gradients can be computed by propagating partial derivatives of the cost function with respect to control parameters through each timestep of the  via the chain rule. However, in \cite{Khaneja2005} Khaneja et al. derive a simple update formula that is correct to first order. In particular one can show that:
\begin{equation}\label{eq:update}
  \begin{split}
\frac{\partial J(U)}{\partial u_{ij}} = -2Re\{\braket{{U_{j+1}^{\dagger}...U_N^{\dagger} U_T}}{i\Delta tH_jU_j...U_1}\\
\braket{U_j...U_1}{U_{j+1}^{\dagger}...U_N^{\dagger} U_T}\} +  \mathcal{O}(\Delta t^2)
  \end{split}
\end{equation}

\section{Optimal Control Problem}\label{ocp}
\subsection{Random Gate Synthesis}
To explore the utility of BCSs, we consider the following Hamiltonian:
\begin{equation}\label{eq:2}
  H(t) = \delta_0H_0 + \sum_{i=1}^n (1 + \delta_i)c_i(t)H_i
\end{equation}
for control Hamiltonians $H_i$, free evolution Hamiltonian $H_0$ and random variables $\delta_i$, that model some small uncertainty in parameters in the Hamiltonian. Such a model might describe a superconducting qubit quantum processor where control amplitudes for the RF pulses vary over time, or a trapped ion quantum computer where the intensity, frequeny, and phase of the laser might drift over time. \needcite(Blueprint for a microwave trapped ion quantum computer) Correlations between different $\delta_i$ might arise if two of the controls have the same noise source. Examples of shared noise sources include $X$ and $Y$ gates in superconducting qubit architectures might use the same AWG and pulse envelope, and diurnal temperature drift of control electronics. \needcite

Given such a Hamiltonian, a threshold approximation fidelity $\mathcal{F}$, and a target gate $U_T$, we can use the technique described in \ref{GRAPE} to generate candidate pulse sequences that enact unitaries $U_i$ that approximate $U_T$, such that $Tr(U_T^{\dagger}U_i) \ge \mathcal{F}$.

In this paper we have modified the update step in \ref{eq:update} to instead use approximately the following gradient:
\begin{align}\label{quadrature}
\int p(\vec{\delta})\frac{\partial J(U(\vec{\delta}))}{\partial u_{ij}} d\vec{\delta}
\end{align}
with $p(\vec{\delta})$ Gaussian distributed. This technique has been used in previous works such as \cite{Goerz2014} to ensure that the optimal control results are robust over a wide range of errors, and we approximate this integral in this paper by using Gaussian quadrature.\needcite Doing this ensures that the family of controls produced by our routine, $U_i$, perform moderately well over a range of control errors that might occur.

\subsection{Channel Approximation}
After using GRAPE or another optimal control routine to synthesize a collection of controls, we must find the weights $w_i$ such that the collection of controls form a BCS as described in (\ref{eq:1}). To do this, for each control $U_i$ we find the unitary error channel $\mathcal{E}_i$ such that $\mathcal{E}_iU_i=U_T$, where $U_T$ is the target gate. If we consider the Pauli-Liouville representation of this error channel, the diagonal terms are the \textit{stochastic} terms that arise from classical uncertainty, while the off-diagonal terms may more generally arise from \textit{coherent} operations. In particular, we see that we can write a convex sum over these channels as:
\begin{align}
 \frac{1}{N} \sum^N_{i=1} w_i \mathcal{E}^{\dagger} (U_T\rho U_T^{\dagger}) \mathcal{E}
\end{align}
Now, to approximate a depolarizing channel we define our optimal control problem to be the following, which minimizes the off-diagonal terms:
\begin{equation}\label{eq:minimization}
  \begin{split}
    &\underset{w_0, ..., w_N}{\textbf{minimize}} \{\sum_{i\neq j}^N|\sigma_i\Lambda(\sigma_j)|^2\}\\
    &\textbf{where}\ \Lambda(\sigma_j) := \sum^N_{i=1}w_i\mathcal{E}_i^{\dagger}\sigma_j\mathcal{E}_i\\
    &\textbf{subject to} \sum_{i=1}^Nw_i = 1
  \end{split}
\end{equation}

@@

Previous authors have considered minimizing the diamond distance to the nearest Pauli or Clifford Channel \cite{Magesan2013}, and while this gives a good theoretical framework, it requires optimizing over the diamond norm, and in particular does not have the restriction that the optimal channel be decomposable into a given family of controls. Our routine, on the other hand, optimizes over an easy to compute sum. In the next section we give a simple example, followed by numerical results for one qubit and two qubits gates in sections \ref{1Q Gates} and \ref{2Q Gates}.

@@

\section{A Simple Example}
As a somewhat trivial example, consider a single-qubit rotation-angle error, such as result from stochastic laser amplitude fluctuations. A BCS may consist of an $X_\pi$ pulse, as well as an $\bar X_\pi$ pulse (i.e., a clockwise and counter clockwise rotation of the qubit). In the case of excess amplitude, the $X_\pi$ pulse will result in an over-rotation error, while the $\bar X_\pi$ pulse results in an \emph{under}-rotation error. When it comes time to perform the target gate in a quantum circuit, one member of the BCS is chosen uniformly at random. This has the effect of decreasing the norm of the noise channel and decorrelating the over-rotation error (Figure \ref{fig:simple_example}). In this simple example, we can solve the minimization problem given by equation \ref{eq:minimization} analytically. In particular, if we choose the weights in \ref{eq:1} such that $\omega_i=1$, and we choose to represent our gates in the vectorized superoperator representation, then:

\begin{equation}
  \begin{gathered}
    \frac{1}{2}(X^*_{\pi + \epsilon}\otimes X_{\pi + \epsilon} + \bar X^*_{\pi + \epsilon}\otimes \bar X_{\pi + \epsilon}) \\  
    = (\sin^2{\frac{\pi + \epsilon}{2}}I\otimes I + \cos^2{\frac{\pi + \epsilon}{2}}X\otimes X)X\otimes X \\
    \approx ((1 - \epsilon^2)I\otimes I + \epsilon^2X\otimes X)X\otimes X
  \end{gathered}
\end{equation}

@@

\section{Numerical Results}\label{numerical}
\subsection{1Q Gates}\label{1Q Gates}
 In this section, we present numerical results on generating one-qubit gates that together with $RZ(\theta$) rotations are universal for one-qubit computation. Our control Hamiltonian is given as: 
\begin{equation}\label{eq:1Qham}
  H = \epsilon\sigma_z + (1 + \delta)(c_x(t)\sigma_x + c_y(t)\sigma_y)
\end{equation}
where $\epsilon \sim \delta \sim \mathcal{N}(0, .001)$ We assume that the errors on $\sigma_x$ and $\sigma_y$ are perfecly correlated, as mentioned in Section \ref{ocp}. In our simulation we chose an total evolution time of $T=\pi$, and a number of steps $N=100$, with a threshold infidelity of $1E-3$.
\begin{figure*}
\centering
\includegraphics[width=\textwidth]{x2.png}
\caption{In the above we have used our method to produce a BCS for a $RX(\frac{\pi}{2})$ pulse, with the Hamiltonian given in \ref{eq:1Qham}. A) shows the sum of the squared norms of the off diagonal terms in the Pauli Transfer Matrix of $\mathcal{E}$. B) gives the corresponding infidelity for each member of the BCS, and the optimal choice of weights.}
\end{figure*}

@@

\subsection{2Q Gates}\label{2Q Gates}
 In this section, we present numerical results on a generating one and two-qubit gates that together with $RZ(\theta)$ rotations are universal for two-qubit computation. Our control Hamiltonian is given as: 
\begin{equation} \label{eq:2Qham}
\begin{split}
H = &\sum_{j=1}^2(\epsilon_j\sigma_z^j + (1 + \delta_j)(c_x^jx(t)\sigma_x^j + c_y^j(t)\sigma_y^j)) \\
&+ \exp{(-i\frac{\sigma_z^1\otimes\sigma_z^2}{4})} 
\end{split}
\end{equation}
We again assume that the standard deviations are $.001$ on all parameters $\delta_j$ and $c^j_i$ and that errors on the single qubit $\sigma_x$ and $\sigma_y$ rotations are perfectly correlated. In this simulation we again had a threshold infidelity of $1E-3$, but we increased the total evolution time to $T=4\pi$, and increased the number of steps to $N=400$ so that the size of each time step was the same as in the one qubit example, however the total evolution time was greater to allow GRAPE more opportunities to find non-trivial pulseshapes. 
\begin{figure*}[t]
\centering
\includegraphics[width=\textwidth]{2Q.png}
\caption{In the above we have used our method to produce a BCS for a ZZ($\frac{\pi}{2}$) entangling gate with controls given by \ref{eq:2Qham}. A) shows the sum of the squared norms of the off diagonal terms in the Pauli Transfer Matrix of $\mathcal{E}$. B) gives the corresponding infidelity for each member of the BCS, and the optimal choice of weights.}
\end{figure*}
